Invasive lionfish present region-wide variation of allometric growth in the

### 2018-05-25 docs/Manuscript.Rmd
All you need to look at is ManuscriptSF.doc
I think I added like one comment to the Manuscript.Rmd file.

---
title: Invasive lionfish present region-wide variation of allometric growth in the
  Western Atlantic
author: "Juan Carlos Villaseñor-Derbez$^1$, Sean Fitzgerald"
header-includes:
- \usepackage{float}
- \floatplacement{figure}{H}
output:
  pdf_document:
    keep_tex: yes
    number_sections: no
    template: peerj_template.tex
institution: "Bren School of Environmental Sciences and Management, University of California Santa Barbara, Santa Barbara, California, U.S."
abstract: "Lionfish (*Pterois volitans/miles*) are an invasive species in the Western Atlantic and the Caribbean. In order to better manage the invasion, we must be able to accurately estimate their total biomass. This work compares length-weight relationships of the invasive lionfish through the invasion range. A review of 17 length-weight relationships reported in 12 peer-reviewed studies shows that lionfish exhibit spatial variation in weight-at-length. The reviewed parameters indicate that, for the same length, lionfish in the Caribbean have lower body mass than in the Atlantic or Gulf of Mexico. This highlights the importance of using site-specific parameters to estimate biomass from length observations. This study also reports a new pair of length-weight parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) for organisms sampled in the central Mexican Caribbean region. These findings can have major implications in management, especially when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs."
keywords: "A, B, C"
---

@@

From this study in the central Mexican Caribbean and the `r length(unique(review$Study))-1` peer-reviewed studies that reported length-weight parameters for *P. volitans* `r dim(review)[1]-1` parameters were identified (Table \ref{tab:all_params}, Fig \ref{fig:all_allo}). Two studies \citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled parameters, while the rest presented pooled results. Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m. Three studies explicitly stated that their organisms were sampled with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014}, and two studies did not specify how organisms were sampled \citep{deleon_2013,darling_2011}. \citet{fogg_2013} use spine-less weight in the length-weight relationship estimation.

@@

>>>>

---
title: Invasive lionfish present region-wide variation of allometric growth in the
  Western Atlantic
author: "Juan Carlos Villaseñor-Derbez$^1$, Sean Fitzgerald"
header-includes:
- \usepackage{float}
- \floatplacement{figure}{H}
output:
  pdf_document:
    keep_tex: yes
    number_sections: no
    template: peerj_template.tex
  word_document: default
keywords: A, B, C
institution: Bren School of Environmental Sciences and Management, University of California
  Santa Barbara, Santa Barbara, California, U.S.
abstract: "Lionfish (*Pterois volitans/miles*) are an invasive species in the Western
  Atlantic and the Caribbean. In order to better manage the invasion, we must be able
  to accurately estimate their total biomass. This work compares length-weight relationships
  of the invasive lionfish through the invasion range. A review of 17 length-weight
  relationships reported in 12 peer-reviewed studies shows that lionfish exhibit spatial
  variation in weight-at-length. The reviewed parameters indicate that, for the same
  length, lionfish in the Caribbean have lower body mass than in the Atlantic or Gulf
  of Mexico. This highlights the importance of using site-specific parameters to estimate
  biomass from length observations. This study also reports a new pair of length-weight
  parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) <!--fix formatting --> for organisms
  sampled in the central Mexican Caribbean region. These findings can have major implications
  in management, especially when estimating biomass available for harvest, predicting
  effects on local ecosystems, or evaluating the effectiveness of removal programs."
---

@@

From this study in the central Mexican Caribbean and the `r length(unique(review$Study))-1` peer-reviewed studies that reported length-weight parameters for *P. volitans* `r dim(review)[1]-1` parameters were identified (Table \ref{tab:all_params}, Fig \ref{fig:all_allo}). Two studies reported gender-level and pooled parameters \citep{aguilarperera_2016,fogg_2013}, while the rest presented pooled results. Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m. Three studies explicitly stated that their organisms were sampled with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014}, and two studies did not specify how organisms were sampled \citep{deleon_2013,darling_2011}. \citet{fogg_2013} use spine-less weight in the length-weight relationship estimation.

@@

<!-- I thought you said the new pair of parameters was LESS interesting to you than the regional differences in length-weight, right?  So I think the "additional" part would be this study, not the regional differences? -->
